---
title: "Factors Impacting Employee Satisfaction"
author: Hai Wen Chen, Avi Mago, William Marshall, Haochen Song, Siddharth Srinivasan
  Swamy, Xuying Zhong
date: "September 25, 2017"
output:
  pdf_document:
    toc: true
    number_sections: true
---

## Introduction

## The Data Set
# Dataset Description
This dataset described the employees of IBM, providing a total of 1470 observations (employees) and 35 variables (information about the employee). The variables can be divided into three groups: Personal Information, Job Information, Satisfaction to the job.
```{r echo=FALSE}
library(knitr)
personal <- data.frame(Variables=c("Age", "DistanceFromHome", "Education",
                                   "EducationField", "Gender", "MaritalStatus",
                                   "NumCompaniesWorked","TotalWorkingYears"),
                       Discription=c("The Employee's age", 
                                     "The distance from home to work", 
                                     "Level of education (1 'Below College', 2 'College', 3 'Bachelor', 4 'Master', 5 'Doctor')",
                                     "The subject of the employee's education (Human Resources, Life Sciences, Marketing, Medical, Other, Technical Degree)", 
                                     "Gender of this employee", "Marital status of this employee (Divorced, Married, Single)",
                                     "The number of companies this employee has worked", "Total number of years this employee has worked since graduation"))

kable(personal, caption = "Personal Information")
```

# The relationship between Attrition and Total Satisfaction
```{r echo=FALSE}
library(dplyr)
IBM <- read.csv("WA_Fn-UseC_-HR-Employee-Attrition.csv")
colnames(IBM)[1] <- "Age"
IBM <- select(IBM, Age:EducationField, EnvironmentSatisfaction:NumCompaniesWorked, OverTime:RelationshipSatisfaction, StockOptionLevel:YearsWithCurrManager) %>% 
  mutate(TotalSatisfaction=EnvironmentSatisfaction+JobSatisfaction+RelationshipSatisfaction+WorkLifeBalance)

library(ggplot2)
Att_TotalSat <- select(IBM, Attrition, TotalSatisfaction)
ggplot(Att_TotalSat,aes(x=Attrition, y=TotalSatisfaction))+geom_boxplot()
```
We can see from the boxplot that there is a relationship between Attrition and Total Satisfaction. Employees who left the company in the end has a lower average total satisfaction and those who stay in the company are more satisfacted with their company. So we can say that by predicting the employee's total satisfaction, we can know whether he is going to leave this company or not.

# Hypothesis 

# Method 

# Analysis 

# Conclusion 

Test 5 - Git Hub App


