---
title: "Factors Impacting Employee Satisfaction"
author: Hai Wen Chen, Avi Mago, William Marshall, Haochen Song, Siddharth Srinivasan
  Swamy, Xuying Zhong
date: "September 25, 2017"
output:
  pdf_document:
    toc: true
    number_sections: true
---

## Introduction

## The Data Set
# Dataset Description
This dataset described the employees of IBM, providing a total of 1470 observations (employees) and 35 variables (information about the employee). The variables can be divided into three groups: Personal Information, Job Information, Satisfaction to the Job in Total.
```{r echo=FALSE}
library(knitr)
personal <- data.frame(Variable=c("Age", "DistanceFromHome", "Education",
                                   "EducationField", "Gender", "MaritalStatus",
                                   "NumCompaniesWorked","TotalWorkingYears"),
                       Type=c("integer","integer","integer","factor","factor","factor","integer","integer"),
                       Description=c("The Employee's age", 
                                     "The distance from home to work", 
                                     "Level of education (1 'Below College', 2 'College', 3 'Bachelor', 4 'Master', 5 'Doctor')",
                                     "The subject of the employee's education (Human Resources, Life Sciences, Marketing, Medical, Other, Technical Degree)", 
                                     "Gender of this employee", "Marital status of this employee (Divorced, Married, Single)",
                                     "The number of companies this employee has worked", "Total number of years this employee has worked since graduation"))

kable(personal, caption = "Personal Information")
```
```{r echo=FALSE}
library(knitr)
jobinfo <- data.frame(Variable=c("Attrition","BusinessTravel","DailyRate","Department","HourlyRate","JobInvolvement",
                                 "JobLevel","JobRole", "MonthlyIncome", "MonthlyRate", "OverTime", "PercentSalaryHike",
                                 "PerformanceRating","StockOptionLevel", "TrainingTimesLastYear","YearsAtCompany",
                                 "YearsInCurrentRole", "YearsSinceLastPromotion","YearsWithCurrManager"),
                      Type=c("factor","factor","integer","factor","integer","integer","integer","factor","integer","integer",
                             "factor","integer","integer","integer","integer","integer","integer","integer","integer"),
                      Description=c("If this employee left the company", "The frquency of business travel", "sth", "The department of this employee (Human Resource, Research & Development and Sales)","sth","1 'Low', 2 'Medium', 3 'High', 4 'Very High'","The level of this employee's job","The position of this employee (Sales Executive, Research Scientist, Laboratory Technician, Manufacturing Director, Healthcare Representative, Manager, (Other))", "The salary of this employee","sth", "If this employee works over time (Yes, No)", "The percentage of salary hike", "1 'Low', 2 'Good', 3 'Excellent', 4 'Outstanding'", "The amount of stock this employee process", "The length of training the employee took last year", "The number of years this employee has been in the company", "The number of years this employee has been in this position","The number of years since last promotion", "The number of years this employee has been with current manager"))

kable(jobinfo, caption = "Job Information")
```

```{r echo=FALSE}
library(knitr)
totals <- data.frame(Variable=c("EnvironmentSatisfaction","JobSatisfaction","RelationshipSatisfaction","WorkLifeBalance" ),
                     Type=c("integer","integer","integer","integer"),
                     Description=c("Satisfaction to the environment (1 'Low', 2 'Medium', 3 'High', 4 'Very High')","Satisfaction to the job (1 'Low', 2 'Medium', 3 'High', 4 'Very High')","Satisfaction to the relationship (1 'Low', 2 'Medium', 3 'High', 4 'Very High')","The work life balance rate (1 'Bad', 2 'Good', 3 'Better', 4 'Best')"))
kable(totals, caption = "Satisfaction to the Job in Total")
```
# The relationship between Attrition and Total Satisfaction
```{r echo=FALSE}
library(dplyr)
IBM <- read.csv("WA_Fn-UseC_-HR-Employee-Attrition.csv")
colnames(IBM)[1] <- "Age"
IBM <- select(IBM, Age:EducationField, EnvironmentSatisfaction:NumCompaniesWorked, OverTime:RelationshipSatisfaction, StockOptionLevel:YearsWithCurrManager) %>% 
  mutate(TotalSatisfaction=EnvironmentSatisfaction+JobSatisfaction+RelationshipSatisfaction+WorkLifeBalance)

library(ggplot2)
Att_TotalSat <- select(IBM, Attrition, TotalSatisfaction)
ggplot(Att_TotalSat,aes(x=Attrition, y=TotalSatisfaction))+geom_boxplot()
```
We can see from the boxplot that there is a relationship between Attrition and Total Satisfaction. Employees who left the company in the end has a lower average total satisfaction and those who stay in the company are more satisfacted with their company. So we can say that by predicting the employee's total satisfaction, we can know whether he is going to leave this company or not.

# Hypothesis 

# Method 

# Analysis 

# Conclusion 

Test 5 - Git Hub App


